Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-08-21 peakcharacterization_manuscript.Rmd
inserting the graph and table

---
title: "Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments"
author: "Robert M Flight, Joshua M Mitchell, Hunter NB Moseley"
date: "`r Sys.time()`"
commit: "`r substr(git2r::branch_target(git2r::head(git2r::repository())), 1, 8)`"
output: 
  redoc::redoc
---

@@

>>>>

---
title: "Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments"
author: "Robert M Flight, Joshua M Mitchell, Hunter NB Moseley"
date: "`r Sys.time()`"
output: 
  redoc::redoc
---

@@

```{r rsd_plots}
drake::loadd(rsd_plot_data)
rsd_plot_data
```

```{r rsd_table}
drake::loadd(rsd_table_data)
knitr::kable(rsd_table_data, digits = 3)
```
